Analysing Constraint Grammars with a SAT-solver

### 2016-03-02 paper/lrec/implementation.tex
change paragraphs to subsections

\paragraph{Preliminaries}

@@

\paragraph{Symbolic sentences}

@@

\paragraph{Applying a rule}

@@

\paragraph{Putting it all together}

@@

\paragraph{Creating realistic readings}

@@

The readings in grammar can be underspecified: for example, the rule
\texttt{REMOVE (verb sg) IF (-1 det)} gives us ``verb sg'' and ``det''.
In contrast, the lexicon only gives us fully specified readings, such
as \texttt{verb pres p2 sg}. We implemented a version where we took
the tag combinations specified in the grammar directly as our
readings, and we could insert them into the symbolic sentences as well.
The shortcut works most of the time, but it is possible to
miss some cases: e.g. \texttt{SELECT Pron + Rel IF (0 Nom)} 
may assume ``pron rel nom'' in one reading, but our method only gives
``pron rel'' and ``nom'' separately. 
In addition, we found that the tag lists in the grammars sometimes
contain errors, such as replacing OR with an AND; using a nonexistent
tag; using a wrong level in a subreading. If we accept those lists as
readings, we will generate symbolic sentences that are impossible, and
won't discover the bug in the grammar.

>>>>

%\paragraph
\subsection{Preliminaries}

@@

%\paragraph
\subsection{Symbolic sentences}

@@

%\paragraph
\subsection{Applying a rule}

@@

%\paragraph
\subsection{Putting it all together}

@@

%\paragraph{Creating realistic readings}
\subsection{Creating realistic readings}
\label{sec:realistic_readings}

@@

The readings in grammar can be underspecified: for example, the rule
\texttt{REMOVE (verb sg) IF (-1 det)} gives us ``verb sg'' and ``det''.
In contrast, the lexicon only gives us fully specified readings, such
as \texttt{verb pres p2 sg}. We implemented a version where we took
the tag combinations specified in the grammar directly as our
readings, and we could insert them into the symbolic sentences as well.
The shortcut works most of the time, but if only take the readings
from the grammar and ignore the lexicon, it is possible to
miss some cases: e.g. \texttt{SELECT Pron + Rel IF (0 Nom)} 
may assume ``pron rel nom'' in one reading, but this method only gives
``pron rel'' and ``nom'' separately. 
In addition, we found that the tag lists in the grammars sometimes
contain errors, such as using a nonexistent tag or using a wrong level
in a subreading. If we accept those lists as readings, we will
generate symbolic sentences that are impossible, and won't discover
the bug in the grammar.
